\centerline{Sudoku}

### 2021-05-25 report/paper.tex
Trying to do a 16x16 sudoku: 2:31:16 it's still running. I could have compiled chrome from source in this time

\newpage
\section{Instructions for running}

@@

>>>>

\subsection{Supporting other board configurations}

In order to support different board configurations that are not of size
$ 9 \times 9 $, we have to make a number of considerations to figure out
which sizes we can support:
First, we know that the highest value that a cell may contain is equal to the
number of cells in each row (or column): in the ``base'' case of the
$ 9 \times 9 $ grid, in fact the highest value is 9.
Now, since we have to fit the exact same number of (distinct) elements both
in a single row, in a single column and in the ``inner box'', we have to
be able to construct such ``inner box'' that allow us to fill them with a number
of element equal to the number or cells per row (or column).

Having these constraints at hand, it is clear how the Sudoku game, with the
(standard) rule set that has been applied through this project is possible only
when the grid is of size $ n \times n $ where $ n $ is a perfect square number
(i.e. $ 9 $ is a perfect square number since it's $ 9 = 3^2 $).
This happens because the ``inner squares'' have to be of size $ \sqrt{n} $
in order to have $ \sqrt{n} $ of them in each row: this is needed because
if we have a square with side of length $ \sqrt{n} $, its area is
$ \sqrt{n}^2 = n $, meaning we can fit in it $ n $ different elements.

\section{Instructions for running}

@@

\begin{figure}[ht]
\centering
\includegraphics[width=0.8\textwidth]{pics/grid_4.png}
\caption{A $ 4 \times 4 $ satisfiable board}
\end{figure}

\begin{figure}[ht]
\centering
\includegraphics[width=0.8\textwidth]{pics/grid_16.png}
\caption{A $ 16 \times 16 $ unsatisfiable board}
\end{figure}
